Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-21 SecDev21/paper.tex
removing old text
further cleanup

TCP is a connection-oriented protocol; a connection between the sender and the receiver must be established before transmitting any data. Furthermore, TCP is a reliable protocol since it guarantees the delivery of all the messages and that they are delivered in the order, they were sent. It also provides error-checking mechanisms to discard and recover any corrupted data.

@@

Generally, every TCP communication session will go through the following three phases (if no error occurs): 1)~opening the connection, 2)~sending and receiving the data, and 3)~closing the connection. The behaviour of the three-phase communication can be described by the state machine given in \cref{Fig:statemachine}. An edge represents a state transition. A transition is either triggered by an explicit action, stated in italics format on the label's edge, for example, \textit{Close}, or is triggered by the arrival of a specific flag/s. An edge-label in the format of $\frac{\ \ x \ \ }{\ \ y \ \ }$ represents the associated flags transmitted with each transition, where $x$ is either send or receive and $y$ refers to the actual flag/s transmitted in response to the action that caused the state transition. An explicit action is either a user-triggered action (through the user's API) or an automatically performed action triggered by a timeout event. The flags are embedded in the header section of a transmitted segment and can be one of the following:
\begin{itemize}
\item \ack: the last message received by the sender is acknowledged.
\item \syn: this flag is sent to establish a connection.
\item \fin: this flag is sent to close the connection.
\item \rst: this flag is sent to reset the connection, often when an error
occurred on one or the other side.
\end{itemize}

@@

Interfacing C and SPARK code is a great opportunity to plug our work in an
existing library, but it is also be a source of errors if it is not done
carefully. In section~\ref{sec:verif} it is explain how we have dealt with these
problems to ensure the quality of our work.

>>>>

TCP is a connection-oriented protocol; a connection between the sender and the receiver must be established before transmitting any data. Furthermore, TCP is a reliable protocol since it guarantees the delivery of all the messages and that they are delivered in the order they were sent. It also provides error-checking mechanisms to discard and recover from corrupted data.

@@

Generally, every TCP communication session will go through the following three phases (if no error occurs): 1)~opening the connection, 2)~sending and receiving the data, and 3)~closing the connection. The behavior of the three-phase communication can be described by the state machine given in \cref{Fig:statemachine}. An edge represents a state transition. A transition is either triggered by an explicit action, stated in italics format on the label's edge, for example, \textit{Close}, or is triggered by the arrival of specific flags. An edge-label in the format of $\frac{\ \ x \ \ }{\ \ y \ \ }$ represents the associated flags transmitted with each transition, where $x$ is either send or receive and $y$ refers to the actual flags transmitted in response to the action that caused the state transition. An explicit action is either a user-triggered action (through the user's API) or an action automatically triggered by a timeout event. The flags are embedded in the header section of a transmitted segment and can be one of the following:
\begin{itemize}
\item \ack: the last message received by the sender is acknowledged.
\item \syn: this flag is sent to establish a connection.
\item \fin: this flag is sent to close the connection.
\item \rst: this flag is sent to reset the connection, often when an error
occurred on one or the other side.
\end{itemize}

@@
